---
title: "Measuring inequalities"
author: "Pearl Ante-Testard"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: default
    highlight: default
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: true
      smooth_scroll: true
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, 
                          encoding   = encoding, 
                          output_dir = here::here("2-initial-analysis/output")
                          )})
---

```{r setup, include=FALSE}
library(mgcv)
library(ggeffects)
library(DHARMa)
library(mgcViz)
library(geepack)
library(msm)
library(tidymv)
#remotes::install_github("stefanocoretta/tidygam@devel")
library(tidygam)
library(cowplot)
library(ggpubr)

```


```{r clean environment, echo=FALSE}

rm(list=ls(all=TRUE))

```

```{r configuration, message=FALSE}

library(here)
source(here::here("2-initial-analysis/R", "0-config.R"))

```

```{r read formatted data, message=FALSE}

#df_analysis <- readRDS(file = here::here("1-data", "2-final",
                      #"enrol_diar_tr_wealth_indiv_svy012.rds"))

# Surveys 1 and 2 (8440 children)
df_analysis_svy12 <- readRDS(file = here::here("1-data", "2-final",
                      "enrol_diar_tr_wealth_indiv_svy012.rds")) %>%
                       filter(svy!=0)

```


```{r data, message=FALSE}

df_analysis_svy12 <- df_analysis_svy12 %>%
  mutate(wealth_rank = rank(wealthscore)/nrow(.),
  block=factor(block),
  wealth_tertile=factor(wealth_tertile),
  diar7d=factor(diar7d),
  Arms=factor(tr_comb, levels = c(0,1), labels = c("Control","Intervention")),
  dummy=rep(1, nrow(.)))

summary(df_analysis_svy12$wealth_rank)

```

## Modelling diarrhea ~ SEP using GAM

```{r gam}

mod_gam = gam(diar7d ~ s(wealth_rank, bs = "cr", by = Arms) +
               s(block, bs = "re", by = dummy), # re is on
               data = df_analysis_svy12,
               family = binomial(link = "log"), method = "REML")
summary(mod_gam)

```

```{r plot gam, message=FALSE}
## partial effects
# control arm
#gratia::draw(mod_gam1)
# intervention arm
#gratia::draw(mod_gam2)

## Probabilities
gam_plot <- plot_smooths(model = mod_gam, series = wealth_rank, 
                         comparison = Arms, transform = exp) +
  #theme(legend.position = "top") +
  labs(x = "Wealth rank",
       y = "Probability of diarrhea") +
       #title = "GAM") +
  theme_bw()

gam_plot <- gam_plot + 
  theme(legend.position = "bottom") 

gam_diff <- get_smooths_difference(mod_gam, wealth_rank, difference = list(Arms = c("Control", "Intervention")))
## codes for get_smooths_difference: https://github.com/stefanocoretta/tidymv/blob/main/R/plotting.R that uses the get_difference function (https://github.com/stefanocoretta/tidymv/blob/main/R/imported-fun.R)
## computes simultaneous CIs which follows Gavin Simpson's: {https://fromthebottomoftheheap.net/2016/12/15/simultaneous-interval-revisited/

plot_diff <- ggplot(gam_diff, aes(wealth_rank, difference, group=group)) +
  geom_hline(aes(yintercept = 0), colour = "#8f5f3f") +
  geom_ribbon(aes(ymin = CI_lower, ymax = CI_upper, fill = sig_diff), alpha = 0.3) +
  geom_line(aes(colour = sig_diff), size = 1) +
  scale_colour_manual(values = c("#e35760", "#6f849c")) +
  scale_fill_manual(values = c("#e35760", "#6f849c")) +
  labs(colour = "significant", fill = "significant") +
  labs(x = " ",
       y = "PD of diarrhea \n(control vs intervention)") +
  #theme(legend.position = "top") +
  theme_bw()

plot_diff <- plot_diff + 
  theme(legend.position = "bottom") 

# to get the PR, the difference was exponentiated
plot_ratio <- ggplot(gam_diff, aes(wealth_rank, exp(difference), group=group)) + 
  geom_hline(aes(yintercept = 1), colour = "#8f5f3f") +
  geom_ribbon(aes(ymin = exp(CI_lower), ymax = exp(CI_upper), fill = sig_diff), alpha = 0.3) +
  geom_line(aes(colour = sig_diff), size = 1) +
  scale_colour_manual(values = c("#e35760", "#6f849c")) +
  scale_fill_manual(values = c("#e35760", "#6f849c")) +
  labs(colour = "significant", fill = "significant") +
  labs(x = "Wealth rank",
       y = "PR of diarrhea \n(control vs intervention)") +
  #theme(legend.position = "top") +
  theme_bw()

plot_ratio <- plot_ratio + 
  theme(legend.position = "bottom") 

#vignette("plot-smooths", package = "tidymv")
#x=plot(ggeffects::ggpredict(mod_gam, terms = c("wealth_rank","Arms")))

plots_gam <- ggarrange(plot_diff, plot_ratio,
            align="hv", ncol = 1, nrow = 2, common.legend = T)

ggarrange(plots_gam, gam_plot,
            align="hv", ncol = 2, nrow = 1)

```


Right-side figure:
It shows that the probability of diarrhea tend to decrease as the relative wealth rank of the children increases for both
control and intervention arms. The intervention arm has a more linear pattern compared to the control arm.

Left-side figures:
Illustrate the prevalence difference (top) and ratio (bottom) of diarrhea between the control and intervention arms. Values above 0 (top) and 1 (bottom) means that the prevalence of diarrhea is greater in the control arm compared to the intervention arm. Values below  0 (top) and 1 (bottom) signify that the prevalence of diarrhea is greater in the intervention arm. We can observe that among those with lower SEP, diarrhea prevalence was significantly higher among the controls. Meanwhile, among those with a relative rank between 0.50 and 0.75, diarrhea was significantly higher in the intervention arm. 

```{r, echo=FALSE, message=FALSE}

#par(mfrow = c(2, 2))
#gam.check(mod_gam1)

#plotQQunif(mod_gam) # left plot in plot.DHARMa()
#plotResiduals(mod_gam, rank = F) 

#plotQQunif(mod_gam2) # left plot in plot.DHARMa()
#plotResiduals(mod_gam2, rank = F) # right plot in plot.DHARMa()

```

## Plotting diarrhea ~ SEP using geeglm

Used wealth_tertile instead of wealth_rank (based on the wealth score) in the model for plotting

```{r plotting geeglm estimates, message=FALSE}

df_control <- df_analysis_svy12 %>%
  filter(Arms == "Control")

df_control$diar7d <- as.numeric(df_control$diar7d)

geemod_c <- geeglm(diar7d ~ wealth_tertile,
                   family = poisson(link="log"), id=block,  corstr='independence', std.err = "san.se",
                   data = df_control)

# Get PR from geemod_c
df_control$prediction <- exp(geemod_c$fitted.values) 
df_control$upper <- exp(geemod_c$fit + 1.96 * coef(summary(geemod_c))[2,"Std.err"])
df_control$lower <- exp(geemod_c$fit - 1.96 * coef(summary(geemod_c))[2,"Std.err"])


df_interv <- df_analysis_svy12 %>%
  filter(Arms == "Intervention")

df_interv$diar7d <- as.numeric(df_interv$diar7d)

geemod_i <- geeglm(diar7d ~ wealth_tertile,
                   family = poisson(link="log"), id=block,  corstr='independence', std.err = "san.se",
                   data = df_interv)

df_interv$prediction <- exp(geemod_i$fitted.values) 
df_interv$upper <- exp(geemod_i$fit + 1.96 * coef(summary(geemod_i))[2,"Std.err"])
df_interv$lower <- exp(geemod_i$fit - 1.96 * coef(summary(geemod_i))[2,"Std.err"])

dat <- rbind(df_control, df_interv)

gee_plot <- ggplot(dat, aes(wealth_tertile, prediction)) +
  geom_errorbar(aes(ymin=lower, ymax=upper, colour = Arms), 
                width = 0.25, size = 1, position = position_dodge(width = 0.4)) +
  geom_point(aes(fill = Arms), shape = 21, size = 3, 
             position = position_dodge(width = 0.4)) +
  #theme(legend.position = "top") +
  labs(x = "Wealth tertiles",
       y = "Prevalence ratio of diarrhea",
       #title = "GEEGLM"
       ) +
  theme_bw() 

gee_plot
```

## Combining the GAM and GEEGLM plots

```{r combining plots}

gam_plot <- gam_plot + 
  theme(legend.position = "right") 

plot_grid(gam_plot, gee_plot, ncol = 1)

```

## RII and SII estimates from the GEEGLM model

Here, used wealth_rank in the model.

```{r rii sii estimates using gee, message = FALSE}

###
# RII < 1 or SII < 0: diarrhea case more likely observed among the poor

## Control

df_control$diar7d <- as.numeric(df_control$diar7d)

geemod_c <- geeglm(diar7d ~ wealth_rank,
               family = poisson(link="log"), id=block,  corstr='independence', std.err = "san.se",
               data = df_control)

## RII
beta_gee_c = geemod_c$coefficients[2]
RII_gee_c = exp(beta_gee_c)
RII_gee_c 

## SII
SII_gee_c = exp(coef(geemod_c)[1]+coef(geemod_c)[2]) - exp(coef(geemod_c)[1])
SII_gee_c


## Intervention

df_interv$diar7d <- as.numeric(df_interv$diar7d)

geemod_i <- geeglm(diar7d ~ wealth_rank,
               family = poisson(link="log"), id=block,  corstr='independence', std.err = "san.se",
               data = df_interv)

## RII 
beta_gee_i = geemod_i$coefficients[2]
RII_gee_i = exp(beta_gee_i)
RII_gee_i 

## SII
SII_gee_i = exp(coef(geemod_i)[1]+coef(geemod_i)[2]) - exp(coef(geemod_i)[1])
SII_gee_i


ineq_estimates <- data_frame(RII_gee_c, RII_gee_i, SII_gee_c, SII_gee_i)
ineq_estimates
```

## 95% CIs

RII CIs: based on Wald interval
SII CIs: based on the delta method using the deltamethod function in the msm package

```{r stand errors gee, message = FALSE}

## Control
# RII
se_b1 = coef(summary(geemod_c))[2,"Std.err"]; #se_b1
RII_low<-exp(beta_gee_c-1.96*se_b1); RII_low
RII_up<-exp(beta_gee_c+1.96*se_b1); RII_up

# SII
# delta method
b <- coef(geemod_c)
v = vcov(geemod_c)
SII_sd = deltamethod(~exp(x1+x2)-exp(x1),b,v) 
# here we require the delta method to estimate the sd of SII
SII_low<-SII_gee_c-1.96*SII_sd; SII_low
SII_up<-SII_gee_c+1.96*SII_sd; SII_up

## Intervention
# RII
se_b1_i = coef(summary(geemod_i))[2,"Std.err"]; #se_b1_i
RII_low_i<-exp(beta_gee_i-1.96*se_b1_i); RII_low_i
RII_up_i<-exp(beta_gee_i+1.96*se_b1_i); RII_up_i

# SII
# delta method
b_i <- coef(geemod_i)
v_i = vcov(geemod_i)
SII_sd_i = deltamethod(~exp(x1+x2)-exp(x1),b_i,v_i) 
# here we require the delta method to estimate the sd of SII
SII_low_i<-SII_gee_i-1.96*SII_sd_i; SII_low_i
SII_up_i<-SII_gee_i+1.96*SII_sd_i; SII_up_i


RII <- c(RII_gee_c, RII_gee_i)
RII_lower <- c(RII_low, RII_low_i)
RII_upper <- c(RII_up, RII_up_i)
SII <- c(SII_gee_c, SII_gee_i)
SII_lower <- c(SII_low, SII_low_i)
SII_upper <- c(SII_up, SII_up_i)
```


```{r estimates with 95% CI}
ineq_tab <- data_frame(RII, RII_lower, RII_upper, SII, SII_lower, SII_upper)
ineq_tab <- as.data.frame(ineq_tab)

row.names(ineq_tab) <- c("Control", "Intervention")
ineq_tab
```

## Estimating diarrhea prevalence by arm

```{r diarrhea by treatment group}

rndr <- function(x, name, ...) {
    if (!is.numeric(x)) return(render.categorical.default(x))
    what <- switch(name)
    parse.abbrev.render.code(c("", what))(x)
}


tab <- df_analysis_svy12 %>%
  mutate(diar7d = fct_drop(factor(diar7d), only = "0"),
         Diarrhea = factor(case_when(diar7d == 1 ~ " ")),
         tx_table1 = factor(tr_comb, labels = c("Control","Intervention"))
         ) %>%
# render
table1(~  Diarrhea | tx_table1, data = ., overall = F,
          render = rndr) 

tab

#set_flextable_defaults(background.color = "black", font.color = "white")
#ft <- flextable(data.frame(tab))
#ft

```


```{r ineq estimates and diarrhea prevalence, message=FALSE}

ineq_tab$prev_diar <- c(6,4)
ineq_tab$Arms <- c("Control", "Intervention")
ineq_tab

```

## Plotting RII/ SII and diarrhea prevalence


```{r, message=FALSE}

ineq_tab$Arms <- factor(relevel(factor(ineq_tab$Arms), ref = "Control"))

a <- ggplot(ineq_tab, aes(prev_diar, RII)) +
  geom_errorbar(aes(ymin=RII_lower, ymax=RII_upper, color = Arms), 
                width = 0.25, size = 1, position = position_dodge(width = 0.4)) +
  geom_point(aes(color = Arms), shape = 21, size = 3, 
             position = position_dodge(width = 0.4)) +
  geom_hline(yintercept = 1, linetype="dotted") +
  scale_color_manual(values = c("#E69F00", "#D55E00")) +
  #coord_flip() +
  #theme(legend.position = "top") +
  labs(x = " ",
       y = "RII (95% CI)",
       title = "Relative Inequalities") +
  guides(col = "none")+
  theme_bw()


b <- ggplot(ineq_tab, aes(prev_diar, SII)) +
  geom_errorbar(aes(ymin=SII_lower, ymax=SII_upper, color = Arms), 
                width = 0.25, size = 1, position = position_dodge(width = 0.4)) +
  geom_point(aes(color = Arms), shape = 21, size = 3, 
             position = position_dodge(width = 0.4)) +
  geom_hline(yintercept = 0, linetype="dotted") +
  scale_color_manual(values = c("#E69F00", "#D55E00")) +
  #coord_flip() +
  #theme(legend.position = "top") +
  labs(x = "Diarrhea prevalence (%)",
       y = "SII (95% CI)",
       title = "Absolute Inequalities") +
  theme_bw()
#b <- b + theme(legend.position = "bottom") 

ineq_plot <- ggarrange(a, b,
            align='h',
            common.legend = T, nrow = 2)

ineq_plot

```

We can observe based on the above figures that both relative and absolute inequalities tend to be smaller when the
diarrhea prevalence is higher (in this case among the controls). This pattern is consistent with other fields such as inequalities in HIV outcomes. 


## Combining the GEEGLM and inequality plots 

```{r}

gee_plot <- ggplot(dat, aes(wealth_tertile, prediction)) +
  geom_errorbar(aes(ymin=lower, ymax=upper, colour = Arms), 
                width = 0.25, size = 1, position = position_dodge(width = 0.4)) +
  geom_point(aes(fill = Arms), shape = 21, size = 3, 
             position = position_dodge(width = 0.4)) +
  #theme(legend.position = "top") +
  labs(x = "Wealth tertiles",
       y = "Prevalence ratio of diarrhea",
       #title = "GEEGLM"
       ) +
  theme_bw() 

gee_plot <- gee_plot + 
  theme(legend.position = "bottom") 

ggarrange(gee_plot, ineq_plot,
            align="hv", ncol = 2, nrow = 1)


```

Left figure:
Prevalence ratio estimates from a GEEGLM model by wealth tertiles and arms. For all tertile groups, PR of diarrhea were higher among the controls. But we only see the error bars not overlapping in the first tertile  - signifying a statistically significant difference between the control and intervention arms. 

Right figures:
Illustrate the inequality indicators - the Relative Index of Inequality (top) and the Slope Index of Inequality (bottomie) in comparison to the diarrhea prevalence by arms.
For both relative and absolute scales, there were significant wealth-related inequalities in diarrhea prevalence disfavoring the poor among the control groups. In the intervention arm, we observed a similar pattern where diarrhea prevalence is higher among the poor but not statistically significant. 
